\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Quiz 2}
\author{Rob Navarro}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}
\noindent
1. Let the following predicates be given. The domain consists of all people. 


F(x) = x is friendly

H(x) = x is helpful 

S(x) = x is a student\\


Express each of the following English sentences in terms of F(x), H(x), S(x),\\
\indent quantifiers, and logical connectives.\\

i. All students are not friendly.

$\forall _x(S(x)\to\neg F(x))$

ii. There are some students who aren't helpful.

$\exists _x(S(x)\to\neg H(x))$

iii. No student is friendly but not helpful.

$\neg\forall _x(F(x)\wedge\neg H(x))$

iv. Every friendly and helpful person is a student. 

$\forall _x((F(x)\wedge H(x))\to S(x))$\\\\

\noindent
2. Let B(x), S(x), and A(x) be the predicates \\\\
B(x) : x is a good basketball player\\
S(x) : x is a good soccer player\\
A(x) : x is a good athlete\\\\
Translate each of the following quantified logic expressions ( provided in the file)  into English considering the domain to consist of all people .\\\\
i. $\forall _x (A(x)\to (S(x)\lor B(x)))$\\
All good athletes are a good soccer player or basketball player. \\\\
ii. $\neg\forall _x(B(x))$\\
Not everyone is a good basketball player.\\ 
iii. $\exists _x((S(x)\wedge\neg B(x))\lor\neg A(x)$\\
There exists a person who is a good soccer player and not a good basketball player, or is not a good athlete. \\
iv. $\exists _x\neg (S(x)\wedge\neg B(x))$\\
There exists a person who is not, a good soccer player and not a good basketball player. \\\\
3. Prove or disprove that $\forall _x(P(x)\to Q(x)) $ and $ \neg\exists _x\neg(\neg Q(x)\to\neg P(x))$ are logically equivalent.\\
$\forall _x(P(x)\to Q(x)) $ \\
$\equiv\neg (\neg\forall _x(P(x)\to Q(x)))$ (Double Negation)\\
$\equiv\neg (\exists _x\neg(\neg P(x)\to Q(x)))$ (5th Logical Equivalence table 7)\\
$\equiv\neg\exists _x\neg(\neg Q(x)\to\neg P(x))$ (2nd Logical Equivalence table 7)\\
This proves that $\forall _x(P(x)\to Q(x)) $ and $ \neg\exists _x\neg(\neg Q(x)\to\neg P(x))$ are logically equivalent. \\\\
8. Use a direct proof to show that the product of  two nonzero rational numbers is also rational.\\
Let $x = \frac {p}{q}$ and $y = \frac {r}{s}$\\
Where $p, q, r,$ and $s$ are all integers and $q$ and $s$ do not equal 0. \\
$x * y = \frac {p}{q} * \frac{r}{s} = \frac{pr}{qs}$\\
Since $p, q, r,$ and $s$ are all integers, $qs\neq 0$ the product is rational. \\\\
9. Use a proof by contraposition to show that If $m^2 + n^2$  is an odd integer, then $m$ is odd or $n$ is odd.\\
Let: p = If $m^2 + n^2$  is an odd integer; q = $m$ is odd or $n$ is odd.\\
This gives us $p\to q$ and the contrapositive is $\neg q\to\neg p$\\
This states that ``If neither $m$ is odd or $n$ is odd, then $m^2 + n^2$  is an even integer.\\
Knowing the definition of an even integer we will let $m = 2k$ and $n = 2l$\\
So, $m^2 + n^2 = (2k)^2 + (2l)^2 = 4k^2 + 4l^2 = 2(2k^2 + 2l^2)$\\
Since $(2k^2 + 2l^2)$ is just some integer this satisfies our contrapositive. This also solves the original proposition that if $m^2 + n^2$  is an odd integer, then $m$ is odd or $n$ is odd.



\end{document}  